---
title: "media_expo_Anti_immi_second_model (Amount_of_media_coverage)"
author: "Chia-Jung Tsai"
date: "8 7 2022"
output:
  html_document: default
  pdf_document: default
---
# Data introduction

## Outcome (from SOEP)
#### dt.rda

- logitidinal data across 2010-2017 and 16 German states (SOEP data) 

- Plj0046: Do you concern the immigration to Germany?
 (1=very concerned, 2= somewhat concerned, 3= not concerned at all)


## predictors 

#### Land_year_longformat.rda (German Federal Official Statistics)

- Frn_rate: Rate of Foreigner in each state by year 2010-2017 
(e.g. (N of Foreigners in Berlin in 2010)/(Total Population in Berlin in 2010)

- Asl_rate: Rate of Asylum applications in each state by year 2010-2017
 (e.g. (N of Asylum applications in Berlin in 2010)/(Total Population in Berlin in 2010)

- Log_Asylum_rate: log number of Asl_rate

- Frn_log: log Number of Foreigners in each state by year 2010-2017 (e.g. log N of Foreigners in Berlin in 2010) 

- Asl_log: log Number of Asylum applications in each state by year 2010-2017 (e.g. log N of Asylum applications in Berlin in 2010)

- Land: German states (16 states) syear: survey year (2010-2017) 


#### Media_by_Gdelt.rda (Gdelt Event database) 
#### state level data
Pub_Year: The publication year of the news article
GE_state: German states, which are equal to "Land" in other dataset

Artl_all: the number of articles of all news events per state per year
Artl_ref: the number of articles of all refugee news events per state per year 
AvgTone_all: the average tone of all news events per state per year
AvgTOne_ref: the average tone of all refugee news events per state per year 

Artl: (N of Refugee Articles per year per state)/(N of all Articles per year per state)
Tone: (average sentiment of Refugee Articles per year per state)-(average sentiment of all Articles per year per state)

#### Media_by_Gdelt_national.rda
#### national level media data!!!!!!!!!!!!!!!!!!

"NA" - mentioned Germany, no city
"Germany (general)" : general Germany news

Artl_all: the number of articles of all news events per state per year
Artl_ref: the number of articles of all refugee news events per state per year 
AvgTone_all: the average tone of all news events per state per year
AvgTOne_ref: the average tone of all refugee news events per state per year 

Artl: (N of Refugee Articles per year per state)/(N of all Articles per year per state)
Tone: (average sentiment of Refugee Articles per year per state)-(average sentiment of all Articles per year per state)


##### Introduction for Gdelt #####
- The Gdelt Event database (1979-2020) 
- 1 row = 1 event
- Select Events mainly by CAMEO Event code (e.g. CAMEO 0233 "Appeal for humanitarian aid" : Make an appeal for, request, or suggest humanitarian assistance. Note: Requests for or suggestions of food, medicine, and related personnel, as well as shelter and protection, are all coded as 0233. Calls by refugees to be let into the territories of other countries (which should be coded as targets) and asylum requests all fit here. Example: Oxfam Canada today called on the world community to help save tens of thousands of Afghan civilians threatened with starvation. )
- All CAMEO codes used here are: 0233, 030, 0333,0343, 075, 0833, 1033, 1223, 1424,1623, 1663, 180, 1822, 184, and 201. Besides, events with "REF" (refugee) code in columns 'Actor1Code' and 'Actor2Code' are also included in the data. 
- "NumArticles" and "AvgTone: In this Event data format, there are two columns "NumArticles" and "AvgTone," which refer the number and the average sentiment all the news articles regarding this event. We aggregate these 2 columns by year ("month" is also available to be used).We aggregate these 2 columns by year ("month" is also available to be used).
- Date : After 2013, data collection date ("DATEADDED") is treated as date of the event news (Gdelt collects data every 15 mins) 
Before 2013, we use the information of the file name (e.g. 20210828.export.CSV.zip ) to recognise the data. The dataset we have so far includes year and month  
- Geo-location: select by columns 'Actor1Geo_FullName', 'Actor2Geo_FullName' and 'ActionGeo_FullName' for the information 'country', 'state', and 'city.' 
- ave_artcl: the average amount of articles relating with refugees in a year (e.g.average of total amount of Jan to Dec in 2010) 
- ave_tone: the average sentiments of articles relating with refugees in a year (e.g.average of average sentiment of Jan to Dec in 2010)


## covariate
### dt_soep_covariate.rda

- pid : personal ID
- hid.x : household ID
- hid.y : household ID
- Land : German states
- sex_re : sex (male=1, female=0)
- higher_edu : combine plg0079_v3 (until 2013) & plg0079_v4 (after2014) (higher edu=1, others=0)
- edu_is97 : isced97 index (higher edu=1, others=0)
- edu_is11 : isced11 index (higher edu=1, others=0)
- edu_ismin : casmin classification (higher edu=1, others=0)
- geburt_v2: birth year
- nationality: Germany=1, others= 0


### model set up:  
- concerns of immigrants= Rate of Asylum seekers*Media exposure (Amount_of_media_coverage)

--with covariates
--with national-level media data

#### Theory: Politicize place assumption (Daniel Hopkins, 2010) people perceive the demographic changes in the surrounding area when the media salience interacts with it 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(lme4)
library(pscl)
library(jtools)
library(haven)
library(plm)
library(gplots)
library(sjPlot)
library(sjmisc)

options(scipen = 999)

```


```{r}
setwd('path to data')
load("Data_Analysis.rda")

```



```{r}
#for revising the figure
dt_n <- dt_2 %>% rename (Log_Asylum_rate=logASLr, Amount_of_media_coverage=Artl, Amount_of_national_media = Artl_national, Edu=edu_is97,  
                         sex =sex_re)

```


## Random slope model with constrained intercept
#### Table A4 & Table A5 in Appendix


## Original model : Log_Asylum_rate*Amount_of_media_coverage
### model1

```{r}
# random slope with constrained intercept

model_1 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + factor(year) +(Log_Asylum_rate*Amount_of_media_coverage-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_1)

exp(coef(model_1)$Land)

re_model1<-ranef(model_1, which="Land", conVar=TRUE)
names(re_model1)<-"The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model1, scales = list(x =list(relation = 'free')))

saveRDS(model_1, file = "model_1.rds")

```
  
### Prediction for random slope with constrained intercept
```{r}
# Odds table for main preditors

tab_model(model_1)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_1 <- rep(fixef(model_1)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_1 <- ranef(model_1)$Land

# Create a new column for the slope
Land_1$slope <- Land_1$`Log_Asylum_rate:Amount_of_media_coverage` + slope_1

# Use the row names to create a Land name column
Land_1$Land <- rownames(Land_1)
Land_1$intercept <- fixef(model_1)['(Intercept)']

ggplot(data=Land_1)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```
  
### marginal effects
```{r}
# marginal effects of year
library(ggeffects)
pd_yr_1<- ggpredict(model_1,term="year")
plot(pd_yr_1)+ylim(c(0,0.5))

```

```{r}
# marginal effects of log Asylum rate/ Article
pd_ASLr_1<- ggpredict(model_1,term="Log_Asylum_rate[all]")
plot(pd_ASLr_1)+ylim(c(0,0.4))

pd_Artl_1<- ggpredict(model_1,term="Amount_of_media_coverage [all]")
plot(pd_Artl_1)+ylim(c(0,0.4))

```

```{r}

ggpredict(model_1,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage")) %>% plot()

ggpredict(model_1,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage"),type = "re") %>% plot()

```
  

   
## Original model+national-level-media-salience  : Log_Asylum_rate*Amount_of_media_coverage + Amount_of_national_media
### model1.1

```{r}
# random slope with constrained intercept

model_1.1 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + Amount_of_national_media + factor(year) +(Log_Asylum_rate*Amount_of_media_coverage-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_1.1)

exp(coef(model_1.1)$Land)

re_model1.1 <-ranef(model_1.1, which="Land", conVar=TRUE)
names(re_model1.1)<-"Figure 3:The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model1.1, scales = list(x =list(relation = 'free')))

saveRDS(model_1.1, file = "model_1_1.rds")

```


### Prediction for random slope with constrained intercept
```{r}
# Odds table for main preditors

tab_model(model_1.1)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_1.1 <- rep(fixef(model_1.1)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_1.1 <- ranef(model_1.1)$Land

# Create a new column for the slope
Land_1.1$slope <- Land_1.1$`Log_Asylum_rate:Amount_of_media_coverage` + slope_1.1

# Use the row names to create a Land name column
Land_1.1$Land <- rownames(Land_1.1)
Land_1.1$intercept <- fixef(model_1.1)['(Intercept)']

ggplot(data=Land_1.1)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```

### marginal effects
```{r}
# marginal effects of year
pd_yr_1.1<- ggpredict(model_1.1,term="year")
plot(pd_yr_1.1)+ylim(c(0,0.5))

```

```{r}
# marginal effects of log Asylum rate/ Article
pd_ASLr_1.1<- ggpredict(model_1.1,term="Log_Asylum_rate[all]")
plot(pd_ASLr_1.1)

pd_Artl_1.1<- ggpredict(model_1.1,term="Amount_of_media_coverage [all]")
plot(pd_Artl_1.1)

```

```{r}

ggpredict(model_1.1,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage")) %>% plot()

ggpredict(model_1.1,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage"),type = "re") %>% plot()

```


## Original model+ controls : Log_Asylum_rate*Amount_of_media_coverage + Edu + nationality + sex + age
### model1.2

```{r}
# random slope with constrained intercept

model_1.2 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + Edu + nationality + sex + age+ factor(year) +(Log_Asylum_rate*Amount_of_media_coverage-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_1.2)

exp(coef(model_1.2)$Land)

re_model1.2 <-ranef(model_1.2, which="Land", conVar=TRUE)
names(re_model1.2)<-"Figure 3:The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model1.2, scales = list(x =list(relation = 'free')))

saveRDS(model_1.2, file = "model_1_2.rds")

```
### Prediction for random slope with constrained intercept
```{r}
# Odds table for main preditors

tab_model(model_1.2)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_1.2 <- rep(fixef(model_1.2)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_1.2 <- ranef(model_1.2)$Land

# Create a new column for the slope
Land_1.2$slope <- Land_1.2$`Log_Asylum_rate:Amount_of_media_coverage` + slope_1.2

# Use the row names to create a Land name column
Land_1.2$Land <- rownames(Land_1.2)
Land_1.2$intercept <- fixef(model_1.2)['(Intercept)']

ggplot(data=Land_1.2)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```


## Original model+ national-level media + controls : Log_Asylum_rate*Amount_of_media_coverage+ Amount_of_national_media + Edu + nationality + sex + age
### model1.3

```{r}
# random slope with constrained intercept

model_1.3 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + Amount_of_national_media + Edu + nationality + sex + age+ factor(year) +(Log_Asylum_rate*Amount_of_media_coverage-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_1.3)

exp(coef(model_1.3)$Land)

re_model1.3 <-ranef(model_1.3, which="Land", conVar=TRUE)
names(re_model1.3)<-"The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model1.3, scales = list(x =list(relation = 'free')))

saveRDS(model_1.3, file = "model_1_3.rds")

```

### Prediction for random slope with constrained intercept
```{r}
# Odds table for main preditors

tab_model(model_1.3)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_1.3 <- rep(fixef(model_1.3)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_1.3 <- ranef(model_1.3)$Land

# Create a new column for the slope
Land_1.3$slope <- Land_1.3$`Log_Asylum_rate:Amount_of_media_coverage` + slope_1.3

# Use the row names to create a Land name column
Land_1.3$Land <- rownames(Land_1.3)
Land_1.3$intercept <- fixef(model_1.3)['(Intercept)']

ggplot(data=Land_1.3)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```


## model with interation with national media  : Log_Asylum_rate*Amount_of_media_coverage+ Log_Asylum_rate*Amount_of_national_media
### model2

```{r}
# random slope with constrained intercept

model_2 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + Log_Asylum_rate*Amount_of_national_media + factor(year) +(Log_Asylum_rate*Amount_of_media_coverage+Log_Asylum_rate*Amount_of_national_media-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_2)

exp(coef(model_2)$Land)

re_model_2 <-ranef(model_2, which="Land", conVar=TRUE)
names(re_model_2)<-"The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model_2, scales = list(x =list(relation = 'free')))

saveRDS(model_2, file = "model_2.rds")

```


### Prediction for random slope with constrained intercept
```{r}
# Odds table for main preditors

tab_model(model_2)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_2 <- rep(fixef(model_2)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_2 <- ranef(model_2)$Land

# Create a new column for the slope
Land_2$slope <- Land_2$`Log_Asylum_rate:Amount_of_media_coverage` + slope_2

# Use the row names to create a Land name column
Land_2$Land <- rownames(Land_2)
Land_2$intercept <- fixef(model_2)['(Intercept)']

ggplot(data=Land_2)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```


### marginal effects
```{r}
# marginal effects of year
library(ggeffects)
pd_yr_2<- ggpredict(model_2,term="year")
plot(pd_yr_2)+ylim(c(0,0.5))

```

```{r}
# marginal effects of log Asylum rate/ Article
pd_ASLr_2<- ggpredict(model_2,term="Log_Asylum_rate[all]")
plot(pd_ASLr_2)

pd_Artl_2<- ggpredict(model_2,term="Amount_of_media_coverage [all]")
plot(pd_Artl_2)

```

```{r}

ggpredict(model_2,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage")) %>% plot()

ggpredict(model_2,term=c("Log_Asylum_rate [all]","Amount_of_media_coverage"),type = "re") %>% plot()

```
  
```{r}

ggpredict(model_2,term=c("Log_Asylum_rate [all]","Amount_of_national_media [0.01, 0.015, 0.02]")) %>% plot()

ggpredict(model_2,term=c("Log_Asylum_rate [all]","Amount_of_national_media [0.01, 0.015, 0.02]"),type = "re") %>% plot()

```

## model with interation with national media +controls : Log_Asylum_rate*Amount_of_media_coverage+ Log_Asylum_rate*Amount_of_national_media + Edu + nationality + sex + age
### model2.1

```{r}
# random slope with constrained intercept

model_2.1 <-glmer(wrimm ~ 1+Log_Asylum_rate*Amount_of_media_coverage + Log_Asylum_rate*Amount_of_national_media  + Edu + nationality + sex + age + factor(year) +(Log_Asylum_rate*Amount_of_media_coverage+Log_Asylum_rate*Amount_of_national_media-1|Land), data=dt_n, family=binomial(link = "logit"), 
                control= glmerControl(optimizer="bobyqa"),nAGQ =0)
summary(model_2.1)

exp(coef(model_2.1)$Land)

re_model_2.1 <-ranef(model_2.1, which="Land", conVar=TRUE)
names(re_model_2.1)<-"The effect of asylum application rate and media salience across regions"
lattice::dotplot(re_model_2.1, scales = list(x =list(relation = 'free')))

saveRDS(model_2.1, file = "model_2_1.rds")

```


### Prediction for random slope with constrained intercept
```{r}
# Odds table for main predictors

tab_model(model_2.1)

```

```{r}

# Extract out the fixed-effect slope for our main effect
slope_2.1 <- rep(fixef(model_2.1)['Log_Asylum_rate:Amount_of_media_coverage'],16)

# Extract out the random-effect slopes for Land
Land_2.1 <- ranef(model_2.1)$Land

# Create a new column for the slope
Land_2.1$slope <- Land_2.1$`Log_Asylum_rate:Amount_of_media_coverage` + slope_2.1

# Use the row names to create a Land name column
Land_2.1$Land <- rownames(Land_2.1)
Land_2.1$intercept <- fixef(model_2.1)['(Intercept)']

ggplot(data=Land_2.1)+
  geom_abline(aes(slope=slope,intercept=intercept,color=Land))+
  theme_minimal()+
  xlim(c(0,2))+ylim(c(-3,3))+
  scale_colour_discrete(breaks=unique(Land_1$Land[order(Land_1$slope, decreasing = TRUE)]))


```


 








